---
title: "project 3"
author: "Mu-Tien, Lee"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("plotly")
#install_github("vqv/ggbiplot")
install.packages('wesanderson')
library(rsconnect)
library(ggbiplot)
library(remotes)
library(dmm)
library(knitr)
library(rmarkdown)
library(MuMIn)
library(tidyverse)
library(caret)
library(corrplot)
library(readxl)
library(caret)
library(ggiraphExtra)
library(knitr)
library(ggplot2)
library(dplyr)
library(ggpubr)
library(rpart.plot)
library(rpart)
library(DT)
rsconnect::setAccountInfo(name='mutien', token='0A2BC4BAAFE09D912EE7CB21B87BBA88', secret='W0xdI1quIfYRq/G7tR+tN1VF2PAoXKOmbkOtpyZf')

rsconnect::deployApp('C:\\Users\\LeeSF\\Desktop\\2020 fall\\ST558\\repo\\ST558_Project3\\Project3') 
```

```{r data}
data <- read.csv("./diabetes_data.csv")
#data2 <- read.csv("diabetes_2")
for( j in 1: nrow(data)){    
  ifelse (data[j,17] == "Positive", data[j,17] <- 1,data[j,17] <- 0)

  for (i in 3:16){
    if (data[j,i] == "Yes") data[j,i] <- 1
    else if (data[j,i] == "No") data[j,i] <- 0
    }
} 
mydata<- data
for (i in 3:16){
  mydata[,i] <- as.numeric(mydata[,i])%>% as.factor()
  data[,i] <- as.numeric(data[,i])
}
data <- as_tibble(data)
mydata$class <- as.factor(mydata$class)
mydata <- as_tibble(mydata)
```

#plot
```{r plot data}
#histogram
ggplot(data=mydata, aes(x=Age))+geom_histogram(aes(fill=class))+labs(title = "Histogram for age seperate by test result")+facet_grid(.~Gender)+scale_fill_discrete(name="Test result", labels=c("Negative", "Positive"))

dataplot <- function(var1, var2){
  t <- paste0("Scatter plots for ", var1, " and ", var2)
  ggplot(data=mydata)+geom_count(aes_string(x=var1, y=var2, color="class",alpha=0.8))+facet_grid(.~Gender)+labs(title = t)+ scale_fill_discrete(name="Test result", labels=c("Negative", "Positive"))
}
dataplot("Polyuria","Polyphagia")
# legend incorrect
names(mydata)
```
#summary table
```{r table}
sumtable <- function(groups, ...){
  sumdata <- data %>% group_by(Gender, class)
  sumdata <-sumdata %>% summarise_all(list(mean))
  datatable(sumdata)
}
sumtable(groups=c("Gender","class"))
```

#unsupervised learning
```{r PCA}
#install.packages("pca3d")
library(pca3d)
for (i in 1:nrow(data)){
  ifelse(data[i,2]=="Male",data[i,2] <- "1", data[i,2]<-"0" )
}
data$Gender <- as.numeric(data$Gender)
PCs <- prcomp(data[,-17], center=TRUE, scale=TRUE)
screeplot(PCs, type = "lines")
pca2d(PCs, 1:2, biplot = TRUE, group = data$class)
```

```{r Clustering}
#install.packages("factoextra")
#install.packages("cluster")
#install.packages("magrittr")
#install.packages("NbClust")
library("cluster")
library("factoextra")
library("magrittr")
library("NbClust")
#k-mean
fviz_nbclust(data[,1:16], kmeans, method = "silhouette")
set.seed(123)
km.res <- kmeans(data[,1:16], 3)
fviz_cluster(km.res, data = data[,1:16],
             ellipse.type = "convex",
             palette = "jco")

#Hierarchical 
HierClust <- hclust(dist(data.frame(data[,1:16])), method = "ward.D2")
fviz_dend(HierClust, k = 4, # Cut in four groups
          cex = 0.5, # label size
          palette = "jco",
          show_labels = FALSE, # color labels by groups
          rect = TRUE # Add rectangle around groups
          )
```

# supervised learning
```{r}
set.seed(615)
train <- sample(1:nrow(mydata), size = nrow(mydata)*0.8)
test <- dplyr::setdiff(1:nrow(mydata), train)
diabetesdataTrain <- mydata[train, ]
diabetesdataTest <- mydata[test, ]

# set up training control, using cross validation with 10 folder
set.seed(615)
trctrl <- trainControl(method = "cv", number = 10)
print(trctrl)
#tree based model
Tree_fit <- train(class~., data = diabetesdataTrain, method = "treebag",
                trControl=trctrl,
                preProcess = c("center", "scale")
                )
Tree_fit$results
plot(Tree_fit)

Tree_pred <- predict(Tree_fit, newdata = diabetesdataTest)
postResample(Tree_pred, diabetesdataTest$class)

#KNN model
KNN <- train(class~., data = diabetesdataTrain, method = "knn",
             trControl=trctrl,
             preProcess = c("center", "scale")
             )
KNN$pred

plot(KNN)

knn_pred <- predict(KNN, newdata = diabetesdataTest)
postResample(knn_pred, diabetesdataTest$class)

#logistic regression model
reg_fit <- train(class~., data = diabetesdataTrain, method = "glm",
                 family="binomial",
                 trControl=trctrl,
                 preProcess = c("center", "scale")
                 )
reg_fit$results
plot(reg_fit)

reg_pred <- predict(reg_fit, newdata = diabetesdataTest)
postResample(reg_pred, diabetesdataTest$class)

```
      reg_model <- eventReactive(input$start_reg{
         trctrl_reg <- trainControl(method = input$reg_trainmethod, 
                                    number = input$reg_num_folders)
         reg_fit <- train(class~., data = diabetesdataTrain, method = "glm",
                          family="binomial",
                          trControl=trctrl_reg,
                          preProcess = c("center", "scale"))
      })

      output$regTrain <- renderTable({
         table(reg_model$reg_fit)
      })

      output$regTest <- renderText({
         Tree_pred <- predict(reg_model$reg_fit, newdata = diabetesdataTest)
         result <- postResample(Tree_pred, diabetesdataTest$class)
         
         paste0("When testing in test data set the Accuracy is ", round(result[1],2), " and Kappa is ", round(result[2],2))
      })
      
                      tuneGrid=expand.grid(n.trees=seq(100,1250,25),
                                     interaction.depth=5:11,
                                     shrinkage=0.1, n.minobsinnode=10
                                     
                                        # Downloadable csv of selected dataset 
   output$downloadData <- downloadHandler(
      filename = function(){paste("diabetesData", ".csv", sep = "")},
      content = function(file){write.csv(downloaddata, file)}

   )